### 2021-12-13 thesis/tex/ICintro.tex
update

\section{Neutrino Detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
% TODO: Write down CC NC equations after 1st paragraph, using N and N’ (N’ can be shower etc).
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
They are of Cherenkov type, which means that they detect 
a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
In the case of CC interactions, this fermion is directly involved in the interaction with the neutrino, either as 
both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.
In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.

If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
into the shower which emit a localized flash of Cherenkov light. This event is referred to as a cascade.
NC interactions tend to be classified as cascades due to the production of a localized hadronic shower
However, CC $\ne$ interactions can also produce a similar localized flash of Cherenkov light, causing them to also contribute 
to the cascade events. A cascade event 
is shown in Fig.~\ref{fig:events_cascade}.

If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
is shown in Fig.~\ref{fig:events_track}.

So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
information in Table~\ref{table:events}, containing classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.

\begin{table}[h]
    \begin{center}
        \begin{tabular}{lcccccc}
            \hline \hline
            Interaction &Track &Cascade\\
            \hline
            CC $\ne$ & 30\%& 70\% \\
            CC $\nm$ & 70\%&30\% \\
            CC $\nt$ & 29\%& 71\%\\
            NC $\nu$ & 24\%& 76\%\\
            \hline \hline
        \end{tabular}
    \end{center}
    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}}\label{table:events}
\end{table}

>>>>

\section{Neutrino Detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade, caused by an interaction in Eq.~\ref{eq:cascade}.}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track, caused by the interaction in Eq.~\ref{eq:track}.} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed, as seen in Eq.~\ref{eq:CC} where an 
incoming neutrino of flavor $\alpha$ scatters of a fermion or hadron $N$, producing a charged lepton $\alpha$,
and $N^\prime$ with charge changed by one unit. 
\begin{align}\label{eq:CC}
    \nu_\alpha + N \to \alpha + N^\prime
\end{align}
This fermion is directly involved in the interaction with the neutrino, either as 
both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.

In NC interactions, shown in Eq.~\ref{eq:NC}, no flavor change can occur, so the fermion leaves with increased energy.
The flavor and charge of the fermion or hadron $N$ interacting with the neutrino is unchanged, but energy 
from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.
\begin{align}\label{eq:NC}
    \nu_\alpha + N \to \nu_\alpha + N^\prime
\end{align}

In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
They are of Cherenkov type, which means that they detect 
a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
into the shower which emit a localized flash of Cherenkov light. This event is referred to as a cascade.
NC interactions tend to be classified as cascades due to the production of a localized hadronic shower
However, CC $\ne$ interactions can also produce a similar localized flash of Cherenkov light, causing them to also contribute 
to the cascade events. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. A cascade event 
is shown in Fig.~\ref{fig:events_cascade} and Eq.~\ref{eq:cascade}, shows the possible interactions causing a cascade event.
Here $N$ denotes an incoming nucleon (consisting of one fermion due to interact with the neutrino), and the resultant $N^\prime$ can be a hadron or
a hadronic shower.
\begin{align}\label{eq:cascade}
    \nu_\alpha + N &\to \nu_\alpha + N^\prime \nonumber \\
    \nu_e + N &\to e + N^\prime  \nonumber \\
    \nu_\tau + N &\to \tau + N^\prime\,.
\end{align}

If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
is shown in Fig.~\ref{fig:events_track}, and and Eq.~\ref{eq:track} shows the possible interactions causing a track event.
\begin{align}\label{eq:track}
    \nm + N \to \mu + N^\prime
\end{align}

So NC interactions and CC $\ne, \nt$ interactions produce cascades, while CC $\nm$ interactions produce tracks. 
The charged secondary $N^\prime$ is then detected (or, in the case of CC $\nt$, a tertiary shower from the $\tau$ decay), and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}. 
However, the detection of the topologies themselves is also not straightforward, and misclassifications are bound to occur.
We see this from classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}, from which we summarize the classification 
information in Table~\ref{table:events}.

\begin{table}[h]
    \begin{center}
        \begin{tabular}{lcccccc}
            \hline \hline
            Interaction &Track &Cascade\\
            \hline
            CC $\ne$ & 30\%& 70\% \\
            CC $\nm$ & 70\%&30\% \\
            CC $\nt$ & 29\%& 71\%\\
            NC $\nu$ & 24\%& 76\%\\
            \hline \hline
        \end{tabular}
    \end{center}
    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}, showing 
    how simulated events where classified.}\label{table:events}
\end{table}
